Untitled

### 2021-12-02 Main_Figures/Figure3.Rmd
edits before submission

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
########################################################################################################################

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
  scale_y_log10()+ggtitle("(d)")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")

>>>>

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1.rds")
########################################################################################################################

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+
  scale_y_log10()+ggtitle("(d)")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("(e)")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2),hjust = 0,face="bold"))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_log10()+ggtitle("(f)")
